
\section*{About}

Each player plays a serial enterpreneur, the goal is to make as much profit as possible by founding startups, pitch them,
find some investors and maybe sell it for a huge profit to a big company.

\section*{Rules}
\subsection*{Preparation}
\begin{enumerate}
\item Every player gets a set of investor cards, from 0 to number of players - 1.
\item Separate the usecase, target audience, action and technology cards
\item Mix 15 of the action cards equaly into the usecase, target audience and technology cards stacks.
\item Shuffle those three stacks.
\end{enumerate}

\subsection*{Game}
\subsubsection*{Round}
\begin{enumerate}
\item If any player has more than tree startups he has to remove them. He can choose which one he wants to keep.
\item Every player gets points for his startups, one for each investor on it divided by the number of player.
\item Every player make his turn.
\item After the pitches, every player hands one of his investor cards covered to every of the other players.
\item Put markers on the new startup equal to the total numbers of investor points he got for his pitch.
\end{enumerate}

\subsubsection*{Players Turn}
\begin{enumerate}
\item Every player draws one card from each stack. If one is an action card he plays it and take another one from that stack.
\item Every player pitches his business idea from those cards, for some seconds, then lay the cards as a small stack in
front of him. Those cards represent a startup.
\end{enumerate}

\subsubsection*{No Cards Left}
If there are no cards left, shuffle the discarded startups again.

\subsubsection*{Finish}
The game ends if one player gets 120 or more points
